---
title: "Regression Models Course Project"
date: "7/15/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive summary

Motor Trend(a magazine about the automobile industry) is Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

- “Is an automatic or manual transmission better for MPG”
- "Quantify the MPG difference between automatic and manual transmissions"

## Exploratory data analyses
```{r}
library(datasets)
data("mtcars")

#Let's take a look at the data to get acquainted with the contents.
head(mtcars)
summary(mtcars)
```

**Average MPG difference between automatic and manual transmissions**
```{r}
mpg_mean <- data.frame(aggregate(list(mean = mtcars$mpg), list(group = mtcars$am), mean), 
      Transmission = c("automatic", "manual"))
mpg_mean
abs(mpg_mean$mean[1] - mpg_mean$mean[2])
```
***MPG difference*** `r abs(mpg_mean$mean[1] - mpg_mean$mean[2])`

**Boxplot to show relation between MPG and Transmission**
```{r fig.height=4, fig.width=5}
boxplot(mpg ~ factor(am), data = mtcars, main = "Transmission Vs MPG", 
        xlab = "Transmission (0=Automatic,1=Manual)")
```

***From the box plot we already see that Manual Transmission is better for MPG.***

Furthermore, we are going to do a t-test, fit models, draw inference, and detail our strategy, then arrive at a conclusion.

## T-Test
```{r}
t.test(mpg~am, mtcars)
```

With p-value of 0.001374 we reject the null Hypothesis. Hence, there is difference in transmission type.

## Fit Model
We fit a linear model with MPG as the outcome and transmission as the predictor
```{r}
fit1 <- lm(mpg ~ factor(am), data = mtcars)
summary(fit1)
```
Here we see that the p-value is very small, However, if take a good look the the value for Multiple R-squared, we will see that the measure of the linear relationship between our predictor variable and our response is very low, this suggests that only `r summary(fit1)$adj.r.squared` of variance in MPG can be attributed to transmission.

## Model Selection
The strategy for model selection is to perform step-wise regression/model selection algorithm.

```{r}
fit2 <- lm(mpg ~ ., data = mtcars)
best_fit2 <- step(fit2, direction = "both", trace = FALSE)
best_fit2$call
```

Now we can fit the linear model and view inference results with the following

```{r}
fit3 <- lm(formula = mpg ~ factor(am) + wt + qsec, data = mtcars)
summary(fit3)
```

Now we see that we have better value of Multiple R-squared showing us that we have a relatively better model

## Residual Plot
We can check if regression assumptions are met with diagnostic plotting:

```{r}
# generate diagnostic plots in 2 x 2 panels
par(mfrow = c(2, 2)); plot(fit3)
```

- Residuals vs Fitted: Here we see that linearity seems not to hold reasonably well
- Normal Q-Q: The points approximately fall on the line and they follow the diagonal fairly close.
- Scale-Location: The residuals begin to spread slightly wider along the x-axis as it passes around 25
- Residuals vs Leverage: No high leverage points.

## Conclusion
The best transmission type for MPG would have to be the manual transmission. we have confirmed by the t-test, and with our final linear model. 

By choosing a manual transmission instead of automatic the MPG will increase by `r summary(fit3)$coefficients[2,1]`, as seen our selected model.

Alternatively we can also say that, by choosing a manual transmission instead of automatic we are 95% confident that our increase in MPG will fall with this range `r confint(fit3)[2]` & `r confint(fit3)[6]`.